Improving the communication and transparency of stock assessment using interactive

### 2018-10-30 manuscript.Rmd
Draft new first paragraph on interactive graphics

In the age of data-intensive science and big data, scientists across many fields are faced with the challenge of synthesizing and communicating information from large and complex data sets. Scientific data are often presented as tabular summaries and static plots, however, seeing patterns in tables can be difficult and static plots are divorced from the underlying data. This limits our ability to explore the underlying data in more detail by, for instance, zooming into areas of interest. New open source tools are bridging this gap by making it easier to build interactive figures [@perkel2018]. In particular, browser-based data visualizations have been playing an increasing prominent role in communicating information on a wide range of topics. Interactive graphics are frequently utilized by media outlets, such as the New York Times, and scientists from a wide range of disciplines are starting to apply interactive visualization tools to explore and communicate their results [@yeatman2018; @tushar2017; @wick2015].

JavaScript libraries, such as D^3^ [@bostock2011], for visualizing data on modern web-browsers now match or exceed the abilities of most platform-specific software and the development of high-level libraries ... plotly ... python ... R

>>>>

In the age of data-intensive science and big data, scientists across many fields are faced with the challenge of synthesizing and communicating information from large and complex data sets. Scientific data are often presented as tabular summaries and static plots, however, seeing patterns in tables can be difficult and static plots preclude detailed explorations of the underlying data. New open source tools are bridging this gap by making it easier to build interactive figures [@perkel2018]. In particular, browser-based data visualizations have been playing an increasing prominent role in communicating information on a wide range of topics. Interactive graphics are frequently utilized by media outlets, such as the New York Times, and scientists from a wide range of disciplines are starting to apply interactive visualization tools to explore and communicate their results [@yeatman2018; @tushar2017; @wick2015]. This trend has been fueled by the development of JavaScript libraries (e.g. D^3^ [@bostock2011], plotly [@plotly], leaflet [@leaflet], highcharts [@highcharts]) that enable the production of dynamic and interactive data visualizations in modern web-browsers. Interfaces to JavaScript libraries have also been developed to allow interactive plots to be coded using commonly used languages such as R [@R] or Python [@python]. By laying the technical infrastructure for creating interactive graphics, these new tools are ushering in a new era of Big Data by facilitating the exploration and communication of complex data and models.

The field of stock assessment is no stranger to complex data and models...
